Connections between $F$-statistics and Principal Component Analysis

### 2022-08-26 talk_leipzig.tex
stuff

\begin{comment}
{
\usebackgroundtemplate{\includegraphics[width=1.4\paperwidth]{figures/bjorklund_art.jpeg}}%
\begin{frame}
	%\frametitle{bla}
	\source{@tombjorklund}
\end{frame}
}
\end{comment}

\begin{comment}

@@

\begin{frame}[plain,c]
\begin{center}
	\Huge Conceptualizing Complex Population Structure remains a major challenge
\end{center}
\end{frame}
\end{comment}

@@

@@

\begin{frame}
	\frametitle{Technical interlude 2: What about projections?}
	Recall that the basic way we project a sample onto a PCA is by multiplying with $\ML$
	\begin{align*}
	F_2(X_i, X_{\text{new}}) &= F_2(Y_i, Y_{\text{new}})\nonumber\\ 
	&= F_2(P_i, P_{\text{proj}}) + F_2(P_{\text{proj}}\ML, Y_{\text{new}})\nonumber\pause\\
	&= \hat{F_2}(P_i, P_j) + {\epsilon(P_i, P_j)} + F_2(P_{\text{proj}}\ML, Y_{\text{new}}) \label{eq:approx}.
	\end{align*}
	\pause
	\begin{alertblock}{Observation}
		Projections adds another error-term that will be small if the projected sample is well-represented by variation of reference sample.
	\end{alertblock}
\end{frame}

@@

@@

\begin{comment}
\begin{frame}
	\frametitle{Thank You!}
	\includegraphics[width=\textwidth]{figures/group_photo.png}
\end{frame}
\end{comment}

>>>>

{
\usebackgroundtemplate{\includegraphics[width=1.4\paperwidth]{figures/bjorklund_art.jpeg}}%
\begin{frame}
	%\frametitle{bla}
	\source{@tombjorklund}
\end{frame}
}

@@

\begin{frame}[plain,c]
\begin{center}
	\Huge Conceptualizing Complex Population Structure remains a major challenge
\end{center}
\end{frame}

@@

\begin{frame}
	\frametitle{Now In Press!}
			\hspace*{-1\beamerleftmargin}
	\includegraphics[width=1.2\textwidth]{talk_figures/paper_head.png}
\end{frame}

@@

\begin{comment}
\begin{frame}
	\frametitle{Technical interlude 2: What about projections?}
	Recall that the basic way we project a sample onto a PCA is by multiplying with $\ML$
	\begin{align*}
	F_2(X_i, X_{\text{new}}) &= F_2(Y_i, Y_{\text{new}})\nonumber\\ 
	&= F_2(P_i, P_{\text{proj}}) + F_2(P_{\text{proj}}\ML, Y_{\text{new}})\nonumber\pause\\
	&= \hat{F_2}(P_i, P_j) + {\epsilon(P_i, P_j)} + F_2(P_{\text{proj}}\ML, Y_{\text{new}}) \label{eq:approx}.
	\end{align*}
	\pause
	\begin{alertblock}{Observation}
		Projections adds another error-term that will be small if the projected sample is well-represented by variation of reference sample.
	\end{alertblock}
\end{frame}

\end{comment}

@@

\begin{frame}
\frametitle{Dimensionality Intuition}
\begin{center}
\includegraphics<1>[width=.5\textwidth]{figures/fig_proj_talk_0.pdf}
\includegraphics<2>[width=.5\textwidth]{figures/fig_proj_talk_1.pdf}
\includegraphics<3>[width=.5\textwidth]{figures/fig_proj_talk_2.pdf}
\includegraphics<4>[width=.5\textwidth]{figures/fig_proj_talk_3.pdf}
\includegraphics<5>[width=.5\textwidth]{figures/fig_proj_talk_4.pdf}
\end{center}	
\end{frame}

@@

\begin{frame}
	\frametitle{Positions Available}
	\begin{columns}
		\begin{column}{0.3\textwidth}
			\includegraphics[width=\textwidth]{talk_figures/erc.png}
		\end{column}
		\begin{column}{0.7\textwidth}
			\textbf{NEADMIX}-project
			\begin{itemize}
				\item Goal: Study Neandertal ancestry through time
				\item 1 PhD and 1 Postdoc position available!
				\item Theory, method development and data analysis
			\end{itemize}
		\end{column}
	\end{columns}
\end{frame}

\begin{frame}
	\frametitle{Thank You!}
	\includegraphics[width=\textwidth]{figures/group_photo.png}
\end{frame}
